%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Dylan Sutro} \\ \vspace{1pt}
    \small (310)-402-3886 $|$ \href{mailto:dsutro1@gmail.com}{\underline{dsutro1@gmail.com}} $|$ 
    % \href{https://www.dylan-sutro.com/}{\underline{dylan-sutro.com}} $|$
    % \href{https://github.com/dsutro}{\underline{github.com/dsutro}}
\end{center}

%-----------Outcome Oriented-----------
\section{Outcome Oriented}
    Seeking opportunities to problem-solve, develop effective solutions to client problems, and expand my programming, hardware, and teamwork skill-sets. Goal of entering the field of unsupervised learning to assist in the discovery of causal features.     

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California Santa Cruz}{Santa Cruz, CA}
      {Bachelor of Science in Computer Engineering}{Expected June 2023}
          \resumeItemListStart
            \resumeItem{Applied Machine Learning - Took courses which focused on designing, building, training, and interpreting various types of machine learning models for different kinds of tasks.}
            \resumeItem{Computer Systems - Rigorous investigation into the sources of complexity for a system and various approaches to creating robust, modular, and secure applications.}
            \resumeItem{Embedded Systems - Extensive coursework in the fields of digital logic, low level programming, micro controller architecture, and processors.}
            \resumeItem{Physics Minor -- Additional classes taken on classical, relativistic, and quantum physics.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analysis Intern}{June 2022 - September 2022}
      {Joby Aviation}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Processed network and flight data to assess simulator accuracy of aircraft conditions and software environment.}
        \resumeItem{Worked with different teams to determine expected performance of software and hardware components of the aircraft.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Verification Intern}{October 2020 – September 2021}
      {Joby Aviation}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Worked in a team environment to deliver bug fixes and feature updates to a diagnostic tool for aircraft components.}\\
        \resumeItem{Learned Aviation standards and certification guidelines as well as procedures for demonstrating reliability of aircraft hardware and software.}
        \resumeItem{Designed, built, and managed python package to supply robust diagnostic modules including a standalone command line interface (CLI) program for end-of-line testing of aircraft computers.}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd
      

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Machine Learning and Music Composition} $|$ \emph{Python, TensorFlow, Jupyter}}{September 2021 -- Present}
          \resumeItemListStart
            % \resumeItem{Investigated parametric models to quantify musical features such as rhythm and melody for detection and generation.}
            % \resumeItem{Explored high order Markov chain solutions to provide context to musical modeling using conditional probability.}
            \resumeItem{Researched various applications of artificial intelligence with respect to music composition including parametric models, probabilistic models, and deep learning with a focus on musical re-synthesis.}
            % \resumeItem{Used swarms and distributed models as an approach to musical intelligence for signal processing.}
            % \resumeItem{Designed and trained a Neural Network to perform multi-layer perception over training sound clips and generate musical compositions.}
            % \resumeItem{Learned various approaches and tools for machine listening -- the ability to extract musical information from sound signals.}
          \resumeItemListEnd

          

      % \resumeProjectHeading
      %     {\textbf{Fretboard Visualizer} $|$ \emph{Python, tkinter}}{January 2020 -- Present}
      %     \resumeItemListStart
      %       \resumeItem{Designed and built command line tool in Python for generating note sequences from user input chord names.}
      %       \resumeItem{Implemented graphical library tkinter to display note sequences as they appear on the fretboard of a guitar.}
      %     \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Frequency Modulation Re-Synthesis Tool} $|$ \emph{Python}}{September 2022 -- March 2023}
          \resumeItemListStart
            \resumeItem{Lead team as product owner of project for Software Engineering Capstone following Agile project management methodologies.}
            \resumeItem{Designed and built in-browser python tool for performing FM re-synthesis (process of recreating a target impulse signal using FM synthesis) using a genetic algorithm.}
          \resumeItemListEnd
         

    \resumeSubHeadingListEnd


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{} \\
     \resumeItemListStart
         \resumeItem{Python: Comfortable using machine learning libraries, graphical utilities, asynchronous programming, and experienced with all design patterns.}
         \resumeItem{C/C++: Applied experience using C/C++ for embedded systems, server/client negotiations, and algorithm analysis and optimization.}
         \resumeItem{SQL: Experience using SQL to manipulate large databases and produce graphical dashboards for meaningful visual inspection.}
         \resumeItem{Databricks, Google Colab, Jupyter: Exposure to various multi-language notebooks managing multiple tasks across different languages in a single environment.}
     \resumeItemListEnd
}}
 \end{itemize}


%-------------------------------------------
\end{document}
